Kinematic Analysis of a Protostellar Multiple System: Measuring the Protostar Masses and Assessing Gravitational Instability in the Disks of L1448 IRS3B and L1448 IRS3A

### 2020-09-16 ms.tex
First push to overleaf. This is after first referee report but before resub

%# document %#
\documentclass[preprint,12pt]{aastex62}
\usepackage{float}
%

%# New commands %#
% molecules
\newcommand{\htcn}{H$^{13}$CN}
\newcommand{\nthp}{N$_2$H$+$}
\newcommand{\ntdp}{N$_2$D$+$}
\newcommand{\cso}{C$^{17}$O}
\newcommand{\ceo}{C$^{18}$O}
\newcommand{\htcop}{H$^{13}$CO$^+$}
\newcommand{\co}{$^{12}$CO}
\newcommand{\sio}{SiO}
\newcommand{\lco}{\co\space      (J = 3$\rightarrow$2)}   % 346.~GHz
\newcommand{\lhtcn}{\htcn\space   (J = 4$\rightarrow$3)}   % 345.339756
\newcommand{\lcso}{\cso\space    (J = 3$\rightarrow$2)}   % 337.061104
\newcommand{\lhtcop}{\htcop\space (J = 4$\rightarrow$3)}   % 346.998347
\newcommand{\lsio}{\sio\space    (J = 7$\rightarrow$6)}   % 347.000031
%                 Continuum                     % 335.5
% misc
\renewcommand{\arcsec}{$^{\prime\prime}$}
\renewcommand{\arcmin}{$^{\prime}$}
\renewcommand{\deg}{$^{o}$}
\renewcommand{\micron}{$\mu$m}

\newcommand{\ab}{$\sim$}
\newcommand{\source}{L1448 IRS3B}
\newcommand{\sources}{L1448 IRS3A\&B}
\newcommand{\ra}{03$^{h}$25$^{m}$36.381$^{s}$}
\newcommand{\dec}{30\deg45\arcmin14\farcs710}
\newcommand{\radec}{RA = \ra, DEC = \dec}
\newcommand{\solm}{M$_{\odot}$}
\newcommand{\x}{$\times$}

% beam sizes
\newcommand{\csobeam}{0\farcs21$\times$0\farcs13} % check this !!!!!!
\newcommand{\siobeam}{0\farcs85$\times$0\farcs52}
\newcommand{\cobeam}{0\farcs19$\times$0\farcs11}
\newcommand{\htcopbeam}{0\farcs21$\times$0\farcs13}
\newcommand{\htcnbeam}{0\farcs21$\times$0\farcs13}
\newcommand{\contbeam}{0\farcs11$\times$0\farcs05}
\newcommand{\contbeamhigh}{0\farcs08$\times$0\farcs05}

%--------------------------------------------------------------------------------------%
%# beginning document %#
%--------------------------------------------------------------------------------------%
\begin{document}
\nocite{*}
%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#
%# authors %#
%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#
% author
\title{Kinematic Analysis of a Gravitationally Unstable Disk: L1448 IRS3B}
\shorttitle{L1448 IRS3B}
\shortauthors{Reynolds et al. (2018)}

\author{
Nickalas K. Reynolds\altaffilmark{1},John J. Tobin\altaffilmark{2},Patrick Sheehan\altaffilmark{2},Claire J. Chandler\altaffilmark{2},Leslie W. Looney\altaffilmark{3},Zhi-Yun Li\altaffilmark{4},Sarah I. Sadavoy\altaffilmark{5},Michael M. Dunham\altaffilmark{6,7},Dominique Segura-Cox\altaffilmark{8},Kaitlin Kratter\altaffilmark{9},Carl Melis\altaffilmark{10},Robert J. Harris\altaffilmark{11},Laura P\^erez\altaffilmark{12}\\\textit{Affiliations included after references}
}

\altaffiltext{1}{Homer L. Dodge Department of Physics and Astronomy, University of Oklahoma, 440 W. Brooks Street, Norman, OK 73019, USA}
\altaffiltext{2}{National Radio Astronomy Observatory, P.O. Box O, Socorro, NM 87801}
\altaffiltext{3}{Department of Astronomy, University of Illinois, Urbana, IL 61801}
\author{}
\altaffiltext{4}{Department of Astronomy, University of Virginia, Charlottesville, VA 22903}
\altaffiltext{5}{Harvard-Smithsonian Center for Astrophysics, 60 Garden St, MS 78, Cambridge, MA 02138}
\altaffiltext{6}{Department of Physics, State University of New York Fredonia, Fredonia, New York 14063, USA}
\altaffiltext{7}{Harvard-Smithsonian Center for Astrophysics, 60 Garden St, MS 78, Cambridge, MA 02138}
\altaffiltext{8}{Department of Astronomy, University of Illinois, Urbana, IL 61801}
\altaffiltext{9}{University of Arizona, Steward Observatory, Tucson, AZ 85721}
\altaffiltext{10}{Center for Astrophysics and Space Sciences, University of California, San Diego, CA 92093}
\altaffiltext{11}{Department of Astronomy, University of Illinois, Urbana, IL 61801}
\altaffiltext{12}{Departamento de Astronom\'ia, Universidad de Chile, Camino El Observatorio 1515, Las Condes, Santiago, Chile}

%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#
%#%# Abstract %#%#
%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#
\begin{abstract}
We present ALMA observations towards a known compact ($<$500 AU separation) triple system, L1448 IRS3B, in Band 7 (879~\micron). We resolve spiral structures in dust continuum in the circum-multiple disk of IRS3B and detect the known wide (\ab2300 AU) companion, IRS3A, within these observations, also resolving possible spiral structure. Using dense gas tracers, \lcso\space and \lhtcn\space, we resolve disk kinematics for both the circum-triple structure and the wide companion with high fidelity.  Further, we use the empirical PV-data and radiative transfer modeling of the molecular line emission to confirm that the disks are in Keplerian rotation with mass estimates of 1.1\solm\space for IRS3B and 1.4\solm\space for IRS3A. Through the continuum models, we estimate the mass of the fragmenting disk of IRS3B to be \ab0.64\solm, indicating this disk is massive enough to be gravitationally unstable. By analyzing the Toomre~Q, we find the IRS3B disk is consistent with a gravitationally unstable disk between the radii \ab100~AU to 600~AU. The embedded tertiary companion, IRS3B-c, is likely \ab0.09\solm. While Toomre~Q analysis of IRS3A, whose disk is measured to be \ab0.08\solm, indicates this source is gravitationally stable.
\end{abstract}

%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#
%#%# Introduction %#%#
%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#
\section{Introduction}
Star formation takes place in dense cores within molecular clouds \citep{1987ARAA..25...23S}, generally found within filamentary structures \citep{2014prpl.conf...27A}. The Perseus Molecular Cloud in particular hosts a plethora of young stellar objects (YSOs) and is nearby \citep[d\ab293 pc; e.g.][]{2018arXiv180803499O} making it an ideal target to study it's protostellar population \citep{2014ApJ...787L..18S,2009ApJ...692..973E}. By observing these YSOs during the first stages of star formation, we can learn about the early evolution of these cores into proto-planetary and/or proto-multiple systems \citep{2014prpl.conf..173L}.

Protostellar systems have been classified into several groups: Class 0, the youngest and most embedded objects characterized by low L$_{bol}$/L$_{submm}$, the less embedded but still dominated by their envelope Class I objects, and Class II objects which have shed their envelope and a protoplanetary disk forms. Most of stellar mass build-up is expected to occur during the Class 0 and Class I phase \citep[$<5\times$10$^{5}$yr; e.g.][]{2018arXiv180711262K,1987IAUS..115....1L} since by the time the system has evolved to Class II, most of the mass of the envelope has been either accreted or blown away by the outflows \citep{2006ApJ...646.1070A}. In order to fully understand star formation and multiple-star formation, it is important to target the youngest of the systems to characterize the initial conditions.

% work on this
% motivate how frequent multple systems are in field stars

\citet{2013ApJ...768..110C} presented a large (33 sources) survey towards known protostellar systems in nearby clouds (d$<$500 pc). This survey was conducted with the Submillimeter Array (SMA) 1.3~mm and 850~\micron\space dust continuum data. Their sample found 21 sources in binaries or higher-order multiplicities (separations \ag50-5000~AU) with a multiplicity frequency and companion fraction of 0.64 and 0.91 respectively. These frequencies were \ab2$\times$\space higher than those found for binary surveys towards Class I sources \citep[0.46 e.g.][]{2008AJ....135.2526C} and \ab4$\times$\space more frequent than surveys targeting main sequence stars \citep[0.21; e.g.][]{1991AA...248..485D} within the 50-5000~AU range. However, this survey suffered from poor spatial resolution, low sensitivity, and only targeted a subset of the known protostellar systems.

In order to better characterize protostellar multiplicity distributions, the VLA Nascent Disk and Multiplicity (VANDAM) survey \citep{2016ApJ...818...73T} targeted all known protostars down to 15 AU scales within the Perseus Molecular Cloud. They confirmed the high multiplicity fraction (MF) on 50-5000~AU scales of \citet{2013ApJ...768..110C} and surpassed them with superior spatial resolution and sensitivities finding the multiplicity fraction of Class 0 protostars \ab57\% (15-10,000~AU scales) and \ab25\% for close ($<$500~AU separation) companions. It was during this survey that L1448 IRS3B, a compact ($<$300~AU) triple system, was discovered. \citet{2016Natur.538..483T} observed this source at 1.3~mm, resolving the spiral arms, kinematic rotation signatures in \ceo, and strong outflows originating from the system.

% fix figure. Try with aplpy just make the triplet and wide aplpy calls without scales
\begin{figure}[H]
\begin{center}
% \includegraphics[width=0.75\textwidth]{img/poster_cont_all_clean.eps}
\includegraphics[width=\textwidth]{img/double_panel_horiz.eps}
\end{center}
\caption{\normalsize The high resolution 879~\micron\space observations of the triple protostellar system L1448 IRS3B and its wide companion IRS3A. The middle image zooms in on the triple structure. The inner binary (IRS3B) is separated by 75 AU and has a tight spiral circumbinary disk with the embedded source 230 AU away from the binary within one of the arms. The right image zooms in on IRS3A (d\ab2300AU), featuring possible spiral structure. The yellow boxes in the left image are location cuts for the two right images of \ab\x3 zoom-ins of the respective sources (middle and right for L1448 IRS3B and IRS3A, respectively). The beam size of each panel is shown in lower right (\contbeam\space using Briggs Robust parameter of 0.5).}\label{fig:contimage}
\end{figure}

L1448 IRS3B (Figure~\ref{fig:contimage}) has a hierarchical configuration, of which the inner binary (separation \ab0\farcs25 (75~AU), denoted -a and -b, respectively)) and the embedded tertiary (separation \ab0\farcs8 (240~AU), denoted -c). A wide (separation \ab 8\arcsec) companion, IRS3A, was also captured within these observations. \citet{2016ApJ...818...73T}\space found evidence for Keplerian rotation and found that the circumtriple disk was likely gravitationally unstable. It is believed there exists three main pathways for forming multiple systems: turbulent fragmentation \citep[1000s of AU; e.g.][]{1989ApJ...347..959A,2010ApJ...708.1585K,2012MNRAS.419.3115B}, thermal fragmentation \citep[1000s of AU; e.g.][]{2013ApJ...764..136B}, and/or gravitational instabilities \citep[100s of AU; e.g.][]{2011MNRAS.410..559M,2009MNRAS.392..413S}.

Here we detail our follow-up observations of L1448 IRS3B with the Atacama Large Millimeter/Submillimeter Array (ALMA), with high resolution and sensitivity. We use kinematic tracers to characterize rotation within the disks of IRS3B and IRS3A. We show our observations and data reduction techniques within Section~\ref{sec:obs}, we discuss our empirical results in Section~\ref{sec:results}, further detail our models and the results produced in Section~\ref{sec:modelresults}, and finally we detail implications of our empirical and model results and discuss future endeavors.

%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#
%#%# Observations %#%#
%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#

\section{Observations}\label{sec:obs}
The ALMA located in Chile, observed \source\space(\radec) in Band 7 (879~\micron) during Cycle 4.
The target was to be observed during two configurations, a long (C40-6) and a compact (C40-3) baseline configuration in order to fully recover the total flux out to \ab5\arcsec\space in addition to resolving the source.

The extended configuration, C40-6, was used on 2016 October 1\&4 with 45 antennas. The baselines sampled span 15 to 3200 (0\farcs05\space agnular resolution to 5\arcsec) for a total of 4495 seconds on source (8052 seconds total). While the compact configuration, C40-3, was observed on 19 December 2016 with 41 antennas. The baselines sampled spanned 15 to 490 meters (0\farcs4 angular resolution to 5\arcsec largest angular scales) for a total of 1335 seconds on source (3098 seconds total).

The correlator was configured to observe \lco, \lcso, \lhtcop, \lhtcn, \lsio, and a broad 2~GHz continuum band centered at 335.5~GHz (894~\micron). A summary of the correlator setup is provided in Table 1. The complex gain calibrator was J0336$+$3218, the bandpass calibrator was J0237$+$2848, and the flux calibrator was the quasar J0238$+$1636.

The raw data were reduced using the Cycle 4 ALMA pipeline using CASA \citep{2007ASPC..376..127M} version 4.7.0. We thoroughly inspected the data and verified the high fidelity. All further processing was done using the CASA 4.7.2 and the reduction sequence is described here. To maximize the sensitivity of the continuum observations, emission free channels from the molecular line spectral windows were added to the continuum after appropriate flagging and splitting of the emission regions was performed. The total bandwidth recovered from this method was \ab1.2~GHz in conjunction with the continuum spectral window bandwidth of 1.875~GHz, yields \ab3~GHz of continuum bandwidth. The observations achieved 0.069~mJy continuum sensitivity, 4~mJy/channel for \co, 3.7~mJy/channel for \cso, 4.5~mJy/channel for \htcn, 4.5~mJy/channel for \htcop, and 0.5~mJy/channel for \sio.

Given the high signal-to-noise (S/N) of the source, we performed self-calibration on the data to further increase the S/N by correcting short timescale phase and amplitude fluctuations. The separate configuration data sets were then concatenated using the task \textit{concat}. The resulting images were generated from this concatenated dataset using Briggs Weighting Robust parameter of 0.5. The beamsize of the continuum image is \contbeam\space (\ab32$\times$15~AU) and \cso\space beamsize is \csobeam\space (\ab79$\times$50~AU).

During the high-resolution execution, an error was made when determining the correlator setup for SiO. The central frequency of the spectral window was adjusted to a lower value (from \ab347.27~GHz to \ab347.01~GHz), outside of the frequency range for SiO. The resulting spectral window was not centered over any visible emission lines; however, the window was fully used for the continuum multi-frequency analysis since no emission lines were discernable.

>>>>

%# document %#
\documentclass[twocolumn, 12pt, trackchanges]{aastex63}
\usepackage{float}
\usepackage{hyperref}
\usepackage{amsmath}
%
\received{June 6, 2020}
\revised{\today}
% \accepted{\today}
\submitjournal{APJL}

%# New commands %#
% molecules
\input{commands.tex}

%-----------

%--------------------------------------------------------------------------------------%
%# beginning document %#
%--------------------------------------------------------------------------------------%
\begin{document}
\nocite{*}
%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#
% author
\title{Kinematic Analysis of a Protostellar Multiple System: Measuring the Protostar Masses and Assessing Gravitational Instability in the Disks of L1448 IRS3B and L1448 IRS3A}
\shorttitle{L1448 IRS3B}
\shortauthors{Reynolds et al.}

\author{Nickalas K. Reynolds}
\affiliation{Homer L. Dodge Department of Physics and Astronomy, University of Oklahoma, 440 W. Brooks Street, Norman, OK 73019, USA}
\author{John J. Tobin}
\affiliation{National Radio Astronomy Observatory, 520 Edgemont Rd. Charlottesville, VA 22901}
\author{Patrick Sheehan}
\affiliation{National Radio Astronomy Observatory, 520 Edgemont Rd. Charlottesville, VA 22901}
\affiliation{Department of Physics and Astronomy, Northwestern University, 2145 Sheridan Road, Evanston, IL 60208, USA}
\author{Sarah I. Sadavoy}
\affiliation{Department of Physics, Engineering Physics \& Astronomy, Queen's University, Kingston, Ontario, Canada}
\author{Kaitlin Kratter}
\affiliation{University of Arizona, Steward Observatory, Tucson, AZ 85721}
\author{Zhi-Yun Li}
\affiliation{Department of Astronomy, University of Virginia, Charlottesville, VA 22903}
\author{Claire J. Chandler}
\affiliation{National Radio Astronomy Observatory, P.O. Box O, Socorro, NM 87801}
\author{Dominique Segura-Cox}
\affiliation{Department of Astronomy, University of Illinois, Urbana, IL 61801}
\author{Leslie W. Looney}
\affiliation{Department of Astronomy, University of Illinois, Urbana, IL 61801}
\author{Michael M. Dunham}
\affiliation{Department of Physics, State University of New York Fredonia, Fredonia, New York 14063, USA}
\affiliation{Harvard-Smithsonian Center for Astrophysics, 60 Garden St, MS 78, Cambridge, MA 02138}
% \author{Carl Melis}
% \affiliation{Center for Astrophysics and Space Sciences, University of California, San Diego, CA 92093}
% \author{Robert J. Harris}
% \affiliation{Department of Astronomy, University of Illinois, Urbana, IL 61801}
% \author{Laura P\'erez}
% \affiliation{Departamento de Astronom\'ia, Universidad de Chile, Camino El Observatorio 1515, Las Condes, Santiago, Chile}

%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#
\begin{abstract}
We present new Atacama Large Millimeter/submillimeter Array (ALMA) observations towards a compact (\ab230~au separation) triple protostar system, L1448 IRS3B, at 879~\micron\space with \contbeam~resolution. Spiral arm structure within the circum-multiple disk is well resolved in dust continuum toward IRS3B, and we detect the known wide (\ab2300~au) companion, IRS3A, also resolving possible spiral substructure. Using dense gas tracers, \lcso, \lhtcop, and \lhtcn, we resolve the Keplerian rotation for both the circum-triple disk in IRS3B and the disk around IRS3A. Furthermore, we use the molecular line kinematic data and radiative transfer modeling of the molecular line emission to confirm that the disks are in Keplerian rotation with fitted masses of \added{$1.19^{+0.13}_{-0.07}$\solm\space for IRS3B-ab, $1.51^{+0.06}_{-0.07}$~\solm\space for IRS3A}, and place an upper limit on the central protostar mass for the tertiary IRS3B-c of 0.2~\solm. We measure the mass of the fragmenting disk of IRS3B to be \ab0.29~\solm\space from the dust continuum emission of the circum-multiple disk and estimate the mass of the clump surrounding IRS3B-c to be 0.07~\solm. We also find that the disk around IRS3A has a mass of \ab0.04~\solm. By analyzing the Toomre~Q parameter, we find the IRS3A circumstellar disk is gravitationally stable (Q$>$2), while the IRS3B disk is consistent with a gravitationally unstable disk (Q$<$1) between the radii \ab200-500~au. This coincides with the location of the spiral arms and the tertiary companion IRS3B-c, supporting the hypothesis that IRS3B-c was formed in situ via fragmentation of a gravitationally unstable disk.
\end{abstract}

%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#
\section{Introduction}\label{sec:intro}
Star formation takes place in dense cores within molecular clouds \citep{1987ARAA..25...23S}, that are generally found within filamentary structures \citep{2014prpl.conf...27A}. The Perseus Molecular Cloud, in particular, hosts a plethora of young stellar objects \citep[YSOs;][]{2014ApJ...787L..18S,2009ApJ...692..973E} and is nearby \citep[d\ab288$\pm$22~pc; e.g.,][]{2018arXiv180803499O, 2019ApJ...879..125Z}, making its protostellar population ideal for high-spatial resolution studies. By observing these YSOs during the early stages of star formation, we can learn about how cores collapse and evolve into protostellar and/or proto-multiple systems, and how their disks may form into proto-planetary systems.

Protostellar systems have been classified into several groups following an evolutionary sequence: Class 0, the youngest and most embedded objects characterized by low L$_{bol}$/L$_{submm}$ \citep[$<5\times10^{-3}$][]{1993ApJ...406..122A} and \tbol\space$\le$70~K, Class I sources which are still enshrouded by an envelope that is less dense than the Class 0 envelope, with T$_{bol}<=650$~K, Flat Spectrum sources, which are a  transition phase between Class I and Class II, and Class II objects, which have shed their envelope and consist of a pre-main sequence star (pre-MS) and a protoplanetary disk. Most stellar mass build-up is expected to occur during the Class 0 and Class I phases \citep[$<5\times10^{5}$~yr; e.g.][]{2018arXiv180711262K,1987IAUS..115....1L}, because by the time the system has evolved to the Class II stage, most of the mass of the envelope has been either accreted onto the disk/protostar or blown away by outflows \citep[][]{2006ApJ...646.1070A, 2014ApJ...784...61O}.

Studies of multiplicity in field stars have observed multiplicity fractions of 63\% for nearby stars \citep[][]{1962AJ.....67R.590W}, 44-72\% for Sun-like stars \citep[][]{1983ARAA..21..343A, 2010ApJS..190....1R}, 50\% for F-G type nearby stars \citep[][]{1991AA...248..485D}, 84\% for A-type stars \citep[][]{2017ApJS..230...15M}, and 60\% for pre-MS stars \citep[][]{1994ARAA..32..465M}. These studies demonstrate the high frequency of stellar multiples and motivates the need for further multiplicity surveys toward young stars to understand their formation mechanisms.

Current theories suggest four favored pathways for forming multiple systems: turbulent fragmentation \citep[on scales \ab1000s of au; e.g.][]{2004ApJ...617..559P, 2004ApJ...600..769F}, thermal fragmentation \citep[on scales \ab1000s of au; e.g.][]{2010ApJ...725.1485O, 2013ApJ...764..136B}, gravitational instabilities within disks \citep[on scales \ab100s of au; e.g.][]{1989ApJ...347..959A, 2009MNRAS.392..413S, 2010ApJ...708.1585K}, and/or loose dynamical capture of cores \citep[\ab10$^{4-5}$~au scales][]{2002MNRAS.336..705B, 2019ApJ...887..232L}. Additionally, stellar multiples may evolve via multi-body dynamical interactions which can alter their hierarchies early in the star formation process \citep{2002MNRAS.336..705B, 2010MNRAS.404..721M, 2012Natur.492..221R}. In order to fully understand star formation and multiple-star formation, it is important to target the youngest systems to characterize the initial conditions.

The VLA Nascent Disk and Multiplicity (VANDAM) survey \citep{2016ApJ...818...73T} targeted all known protostars down to 20~au scales within the Perseus Molecular Cloud using the Karl G. Jansky Very Large Array (VLA) to better characterize protostellar multiplicity. They found the multiplicity fraction (MF) of Class 0 protostars to be \ab57\% (15-10,000~au scales) and \ab28\% for close companions (15-1,000~au scales), while, for Class I protostars, the MF for companions (15-10,000~au scales) is 23\% and 27\% for close companions (15-1,000~au scales). This empirical distinction in MF motivates the need to observe Class 0 protostars to resolve the dynamics before the systems evolve. It was during this survey that the multiplicity of L1448 IRS3B, a compact (\ab230~au) triple system, was discovered. \citet{2016Natur.538..483T} observed this source at 1.3~mm, resolving spiral arms, kinematic rotation signatures in \ceo, \tco, and \htco, with strong outflows originating from the IRS3B system.

L1448 IRS3B has a hierarchical configuration, which features an inner binary (separation 0\farcs25$\approx$75~au, denoted -a and -b, respectively) and an embedded tertiary (separation 0\farcs8$\approx$230~au, denoted -c). The IRS3B-c source is deeply embedded within a clump positioned within the IRS3B disk, thus we reference the still forming protostar as IRS3B-c and the observed compact emission as a ``clump'' around IRS3B-c. \citet{2016ApJ...818...73T}\space found evidence for Keplerian rotation around the disks of IRS3B and IRS3A. They also found that the circum-triple disk was likely gravitationally unstable.

Theory suggests that during stellar mass assembly, when the disk is forming via conservation of angular momentum \citep{1976ApJ...210..377U, 1984ApJ...286..529T, 2014prpl.conf..173L}, gravitational fragmentation should occur if the disk is massive \citep{1989ApJ...347..959A, 1999ApJ...525..330Y, 2010ApJ...710.1375K}. These fragmentation events, if large enough, can form stellar multiples and is a possible pathway for the formation of compact (\ab100s of au scales) multiple systems. Since observations show that the youngest systems, like L1448 IRS3B, have higher disk masses than their more evolved counterparts \citep{2020ApJ...890..130T}, we would also expect disk fragmentation to be the most common mechanism in the Class 0 stage.

The wide and compact proto-multiple configurations of IRS3A and IRS3B contained within a single system provides a test bed for multiple star formation pathways to determine which theories best describe this system. Here we detail \added{our follow-up observations to \citet{2016Natur.538..483T} of L1448 IRS3B with the Atacama Large Millimeter/submillimeter Array (ALMA) in Band 7, with $2\times$~higher resolution and $6\times$~higher sensitivity. We resolve the kinematics toward both IRS3B and IRS3A with much higher fidelity that the previous observations, enabling us to characterize the nature of the rotation in the disks, measure the protostar masses, and characterize the stability of both disks.} We show our observations of this system and describe the data reduction techniques in Section~\ref{sec:obs}, we discuss our empirical results and our use of molecular lines in Section~\ref{sec:results}, we then refine the molecular lines used to trace disk kinematics in Section~\ref{sec:keprotation}, we further detail our models and the results in Section~\ref{sec:kmodelresults}, and we interpret our findings in Section~\ref{sec:discussion}, where we discuss the implications of our empirical and model results and future endeavors.

%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#
\section{Observations}\label{sec:obs}
\explain{Bulk of observation explanations was moved to appendix. Particularly the content surrounding self calibration.}
We observed L1448 IRS3B with ALMA in Band 7 (879~\micron) during Cycle 4 in two configurations, an extended (C40-6) and a compact (C40-3) configuration in order to fully recover the total flux out to \ab5\arcsec\space angular scales in addition to resolving the structure in the disk. C40-6, was used on 2016 October 1~and~4 with 45 antennas. The baselines ranged from 15 to 3200~meters, for a total of 4495 seconds on source (8052 seconds total) for both executions. C40-3, was used on 19 December 2016 with 41 antennas. The baselines covered 15 to 490 meters for a total of 1335 seconds on source (3098 seconds total).

The complex gain calibrator was J0336$+$3218, the bandpass calibrator was J0237$+$2848, and the flux calibrator was the monitored quasar J0238$+$1636. The observations were centered on IRS3B. IRS3A, the wide companion, is detected further out in the primary beam with a beam efficiency \ab60\%).

We summarize the observations in Tables~\ref{table:obssummary1}~and~\ref{table:obssummary2} and further detail our observations and reductions in Appendix~\ref{sec:appobs}.

It should also be noted there is possible line blending of \lhtcn\space and \lsot\space\citep{1997Icar..130..355L} (Table~\ref{table:obssummary2}). The \sot\space line has an Einstein A coefficient of 2.4$\times10^{-4}$~s$^{-1}$ with an upper level energy of 93~K, demonstrating the transition line strength could be strong. \sot\space provides another shock tracer which could be present toward the protostars. We label \htcn\space and \sot\space together for the rest of this analysis to emphasize the possible line blending of these molecular lines. Additionally, the \co\space and \sio\space emission primarily trace outflowing material and analysis of these data is beyond the scope of this paper, but the integrated intensity maps of select velocity ranges are shown in in Appendix~\ref{sec:coemission}~and~\ref{sec:sioemission}. The results of this analysis are summarized for each of the sources in Table~\ref{table:obssummary3}.

%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#%#
\section{Results}\label{sec:results}
\subsection{879~\micron~Dust Continuum}\label{sec:dcont}
The observations contain the known wide-binary system L1448 IRS3A and L1448 IRS3B and strongly detect continuum disks towards each protostellar system (Figures~\ref{fig:contimage}~and~\ref{fig:zoomincont}). We resolve the extended disk surrounding IRS3A (Briggs robust weight $=0.5$: Figure~\ref{fig:contimage}, superuniform: Figure~\ref{fig:widesuperuniform}) and marginally resolve possible spiral arm substructure.

\subsubsection{IRS3B}
We resolve the extended circum-multiple disk of IRS3B and the spiral arm structure that extends asymmetrically to \ab600~au North-South. Figure~\ref{fig:zoomincont}\space shows a zoom in on the IRS3B circumstellar disk, showing clear substructures. Furthermore, we observe the three distinct continuum sources within the disk of IRS3B as identified by \citet{2016Natur.538..483T}, but with our superior resolution and sensitivity (\ab2$\times$\space higher), our observations are able to marginally resolve smaller-scale detail closer to the inner pair of sources, IRS3B-a and -b (Figure~\ref{fig:zoomincont}). We now constrain the origin point of the two spiral arm structures. Looking towards IRS3B-ab, we notice a decline in the disk continuum surface brightness in the inner region, north-eastward of IRS3B-ab. We also observe a ``clump'' \ab50~au East of IRS3B-b. However, given that this feature is located with apparent symmetry to IRS3B-a, it is possible that the two features (``clump'' and IRS3B-a) are a part of an inner disk structure as there appears a slight deficit of emission located between them (``deficit''), while IRS3B-b is just outside of the inner region. \added{While this so-called ``clump'' could just be a surface brightness variation in the spiral substructure, the source was observed in \citet{2016ApJ...818...73T}\space at longer wavelengths.}

\subsubsection{IRS3B-ab}
To best determine the position angle and inclination of the circum-multiple disk, we first have to remove the tertiary source that is embedded within the disk using the \textit{imfit} task in CASA by fitting two 2-D Gaussians with a constant emission offset (detailed fully in Appendix~\ref{sec:tertsub}). We fit the semi-major and semi-minor axis of the IRS3B-ab disk with a 2-D Gaussian using the task \textit{imfit} in CASA. To fit the general shape of the disk and not fit the shape of the spiral arms, we smooth the underlying disk structure (taper the uv visibilities at 500~k$\lambda$ during deconvolution using the CASA \textit{clean} task), yielding more appropriate image for single 2D Gaussian fitting.

From this fit, we recovered the disk size, inclination, and position angle, which are summarized in Table~\ref{table:obssummary3}. The protostellar disk of IRS3B has a deconvolved major axis and minor axis FWHM of \added{1\farcs73$\pm$0\farcs05\space and 1\farcs22$\pm$0\farcs04\space} (497$\pm$17~au\space $\times$\space 351$\pm$12~au), respectively\deleted{, corresponding to an average continuum disk radius of \ab248.5~au (assuming the disk is symmetric)}. This corresponds to an inclination angle of 45.0\deg$^{+2.2}_{-2.2}$\space assuming the disk is symmetric and geometrically thin, where an inclination angle of 0\deg\space corresponds to a face-on disk. We estimate the inclination angle uncertainty to be as much as 25\% \space by considering the south-east side of the disk as asymmetric and more extended. The position angle of the disk corresponds to 28$\pm$4\deg\space East-of-North. 
% ((1 / (y * (1 - (x^2 / y^2)) ^ 0.5) * g ) ^ 2 + (x / (y^2 * (1 - (x^2 / y^2)) ^ 0.5) *  h) ^ 2) ^0.5 * acos(x/y), where x=351, y = 497, g=12, h=17

\subsubsection{IRS3B-c}
In the process of removing the clump around the tertiary companion IRS3B-c, we construct a model image of this clump that can be analyzed through the same methods. We recover a deconvolved major axis and minor axis FWHM of 0\farcs28$\pm$0\farcs05\space and 0\farcs25$\pm$0\farcs04\space (80$\pm$17~au\space $\times$\space 71$\pm$12~au), respectively, corresponding to a radius \added{\ab40~au (assuming the disk is symmetric)}. This corresponds to an inclination angle of 27.0\deg$^{+19}_{-19}$\space and we fit a position angle of 21$\pm$1\deg\space East-of-North. We note the inclination estimates for IRS3B-c may not be realistic since the internal structure of the source (oblate, spherical, etc.) cannot be constrained from these observations, thus the reported angles are assuming a flat, circular internal structure, similar to a disk.
% ((1 / (y * (1 - (x^2 / y^2)) ^ 0.5) * g ) ^ 2 + (x / (y^2 * (1 - (x^2 / y^2)) ^ 0.5) *  h) ^ 2) ^0.5 * acos(x/y), where x=71, y = 80, g=12, h=17

\subsubsection{IRS3A}
The protostellar disk of IRS3A has a FWHM radius of \ab100~au and has a deconvolved major axis and minor axis of \added{0\farcs69$^{0.01}_{0.01}$\space and 0\farcs25$^{0.1}_{0.1}$}\space(197$\pm$3~au $\times$\space 72$\pm$3~au), respectively. This corresponds to an inclination angle of 68.6\added{$\pm$1.2}\deg\space assuming the disk is axially symmetric. The position angle of the disk corresponds to 133$\pm$1\deg\space East-of-North. \added{We marginally resolve two emission deficits one beamwidth off IRS3A, along the major axis of the disk. The potential spirals appear to originate along the minor axis of the disk; however, due to the reconstructed beam elongation along the semi-minor axis of the disk, we cannot fully resolve the substructure of the disk around IRS3A.}
% ((1 / (y * (1 - (x^2 / y^2)) ^ 0.5) * g ) ^ 2 + (x / (y^2 * (1 - (x^2 / y^2)) ^ 0.5) *  h) ^ 2) ^0.5 * acos(x/y), where x=72,  y = 197, g=3, h=5

\subsection{Disk Masses}\label{sec:diskmass}
The traditional way to estimate the disk mass is via the dust component which dominates the disk continuum emission at millimeter wavelengths. If we make the assumption that the disk is isothermal, optically thin, \added{without scatter}, and the dust and gas are well mixed, then we can derive the disk mass from the equation:

\begin{equation}\label{eq:dustmass}
    M_{dust} = \frac{D^2 F_{\lambda}}{\kappa_{\lambda}B_{\lambda}(T_{dust})}
\end{equation}
where $D$ is the distance to the region (288~pc), $F_{\lambda}$\space is the flux density, $\kappa_{\lambda}$\space is the dust opacity, $B_{\lambda}$\space is the Planck function for a dust temperature, and $T_{dust}$\space is taken to be the average temperature of a typical protostar disk. The $\kappa_{\lambda}$\space at $\lambda$ = 1.3~mm was adopted from dust opacity models with value of 0.899~cm$^2$~g$^{-1}$, typical of dense cores with thin icy-mantles \citep{1994AA...291..943O}. We then appropriately scale the opacity:
